Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-22 paper.tex
Proved the existence of i^n_n+1 on the 1-skeleton

We denote by $\gromov{{-}}{{-}}{{-}}$ the Gromov product on $G \union
\boundary G$. Using $\newdist$ we extend the Gromov product to $K$:

@@

\begin{definition}
  We say that $G$ satisfies $\ddag_M$ if there exists a number $L$ such that,
  for any $n$ and any $x$ and $y$ in $S_n$ with $\dist(x,y) \leq M$, $x$ and
  $y$ are connected by a path of length at most $L$ in the complement of the
  ball with radius $\dist(x,y) - 3\delta$ with centre $1 \in G$.
  \todo{$3\delta$?}
\end{definition}

@@

  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
\end{lemma}

@@

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_M$ for $M = ?$. Then there exists $k$
  such that for $n$ sufficiently large there is a map
  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
  conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_k\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
  $K_n$, let $\alpha$ be a geodesic with $\dist(x, \alpha(n)) \leq 4\delta$ and
  let $i^n_{n+1}(x)$ be any vertex of the minimal simplex of $K_{n+1}$
  containing $p^\infty_{n+1}(\gamma_x(\infty))$. Then the second claimed
  property follows from \todo{why?}

  For an edge $e$ of $K_n$, the distance between the images of the end points
  of $e$ under $i^n_{n+1}$ is at most \todo{?} and it follows that \todo{prove
  this}.
\end{proof}

>>>>

We denote by $\gromov{{-}}{{-}}{{-}}$ the Gromov product on $G \union
\boundary G$. Using $\newdist$ we extend the Gromov product to $K$:
\todo{This looks shit.}

@@

\begin{definition}
  We say that $G$ satisfies $\ddag_M$ if there exists a number $L$ such that,
  for any $n$ and any $x$ and $y$ in $S_n$ with $\dist(x,y) \leq M$, $x$ and
  $y$ are connected by a path of length at most $L$ in the complement of the
  ball with radius $\dist(x,y) - \delta$ with centre $1 \in G$.
\end{definition}

@@

  Furthermore, $\dist(x, \alpha(\dist(e,x))) \leq 4\delta$.
  \todo{Since I'm assuming ideal triangles are delta-slim, 2delta should be
  delta and 4delta should be 2delta.}
\end{lemma}

@@

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_{D + 8\delta+2}$. Then there exists $L$
  such that for $n$ sufficiently large there is a map $i^n_{n+1}\from \Skel_1
  K_n \to \Skel_1 K_{n+1}$ satisfying the following conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 4\delta+1$,
      and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  Let $n_0$ and $L$ be the numbers given by the condition $\ddag'_{D + 8\delta
  + 2}$ and let $n \geq n_0$.

  First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
  $K_n$, let $\gamma_x$ be a geodesic with $\dist(x, \gamma_x(n)) \leq 4\delta$
  and let $i^n_{n+1}(x)$ be $\gamma_x(n+1)$, which is a vertex of a simplex
  containing $p^\infty_{n+1}(\gamma_n(\infty))$. Then $\dist(x, i^n_{n+1}(x))
  \leq 4\delta + 1$, as required by the second condition.

  For an edge $e$ of $K_n$ with end points $x_1$ and $x_2$, the distance
  $\dist(x_1, x_2)$ is at most $D + 8\delta + 2$. It follows that there is a
  path $\alpha$ from $\gamma_{x_1}(\infty)$ to $\gamma_{x_2}(\infty)$ in
  $\boundary G$ so that $p^\infty_{n+1}\composed\alpha$ admits a simplicial
  approximation connecting $i^n_{n+1}(x_1)$ to $i^n_{n+1}(x_2)$ after at most
  $L$ subdivisions. Define $i^n_{n+1}$ to be this simplicial map on $\sd^L e$.

  This process defines a map $i^n_{n+1}\from \Skel_1 K_n\to \Skel_1 K_{n+1}$
  with the required properties.
\end{proof}
